\section{Future Work}
\subsection{Attribute Grammar}
future work blah
\subsubsection{Annotating Context Free Grammars with Attributes}

Context free grammars can be annotated with synthesized attributes using a
straight forward process if the types of attributes are reasonably restricted.
For this paper we allow three types of attributes: 1) production choice, eg.
which production for the non-terminal was chosen, 2) scalar attributes, eg. the
value of a token or the name of a token, 3) set attributes, eg. collections of
scalar attributes. 

why the restrictions are reasonable 

exact bound on what can be expressed

\paragraph{Algorithm Sketch}

All possible attributes are synthesized

Conditions are proposed based, and tested against operational inputs. Only those
conditions which pass all operational inputs are kept.

Attributes un-used by final conditions are pruned.

\subsection{CFG Stats}
blargh
\subsection{Mutation Fuzzing}
The current implementation of mutation fuzzing in Fuzzbuzz is a great
foundation for future work. There is a clear path to integrating CFG
stats and attribute grammars into the generation process. By
integrating these methods, it is likely that Fuzzbuzz will be able to
prune the mutation space to sufficient level to generate mutations
that are effective at fault discovery.

\section{Conclusion}
Hello, this project is good.

This project is a work in progress

We have discovered that this solution is good from a blackbox
perspective.


%-----------------------------------

Fuzzbuzz explores a wide range of fuzzing techniques. However, it is
still very much a work in progres. While it is not yet a
fully featured fuzzing framework, it still provides a valuable toolset
for anyone interested in fuzz testing.

Tim will now talk about blackbox stuff.


